The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             The profile along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
     }
    \label{fig__profile}
  \end{figure}

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of profiles around $z=3.7$ kpc.\
             The sharp pressure jump and dense shell at $z=3.61$ kpc\
             indicate that the innermost bubbles are an expanding reverse shock.\
     }
    \label{fig__profile}
  \end{figure}
